Precision calculations for cosmic shear

### 2017-02-08 limber2.tex
MK edits

We compute the spherical-sky weak-lensing power spectrum of the shear and
convergence. We discuss various approximations, such as flat-sky, first- and
second-order Limber equations for the projection. We find that the impact of adopting 
these approximations are negligible when constraining cosmological parameters from 
current weak lensing surveys.
This is demonstrated using data from the Canada-France-Hawaii Lensing Survey (CFHTLenS). 
We find that the reported tension with Planck CMB temperature anisotropy results cannot be alleviated, in
contrast to the recent claim made by \citet{2016arXiv161104954K}. 
For future large-scale surveys with unprecedented precision, we show that the spherical
second-order Limber approximation will provide sufficient accuracy, as it is in 
agreement with the full projection at the percent level for $\ell > 3$.  
In the spirit of reproducible research, our numerical implementation of all approximations
and the full projection are publicly available within the package
\texttt{nicaea} at \texttt{http://www.cosmostat.org/software/nicaea}.

@@

The measurement of weak gravitational lensing by large-scale structures
provides a powerful cosmological probe of dark matter, dark energy, and
modifications to gravity.  As such it is the primary science goal of several
current (KiDS, DES, HSC\footnote{KiDS: \href={http://kids.strw.leidenuniv.nl}, DES: \href={http://www.darkenergysurvey.org}, HSC: \href={http://hsc.mtk.nao.ac.jp/ssp/}})
and future (Euclid, LSST, WFIRST\footnote{Euclid: \href={http://sci.esa.int/euclid}, LSST: \href={http://www.lsst.org}, WFIRST: \href={http://wfirst.gsfc.nasa.gov}}) surveys.
%(Kilo-Degree Survey, KiDS \citet{kuijken/etal:2015}, Dark Energy Survey, DES, \citet{abbott/etal:2016}, Hyper-Suprime Camera Survey, HSC\footnote{HSC; \href={http://hsc.mtk.nao.ac.jp/ssp/}}) and future (Euclid, \citet{2011arXiv1110.3193L}, LSST, \citet{chang/etal:2013}, WFIRST\footnote{WFIRST; \href={http://wfirst.gsfc.nasa.gov}}) large-scale surveys.
Interest in the results from these surveys is high as statistically significant
deviations have been found between the cosmological parameter constraints from
the CMB Planck experiment \citep{2015arXiv150201589P} in comparison to weak
lensing constraints from both the Kilo-Degree Survey \citep[KiDS;][]{KiDS-450}
and the Canada-France-Hawaii Telescope Lensing Survey
\citep[CFHTLenS;][]{joudaki/etal:2016}.  If the source of this tension is not
a result of so-far unconsidered sources of systematic errors in one or all
experiments, extensions to the standard flat $\Lambda$CDM cosmological models
need to be considered. \citet{joudaki/etal:2017} have shown, for example, that
the tension can be resolved with an evolving dark energy model.

In the era of the upcoming large-scale surveys that will provide measurements of
cosmic shear with unprecedented precision, one needs to revisit the theoretical
predictions of the observables to ensure that the accuracy of the
models meet the accuracy of the upcoming data. In this paper, we examine the widely used Limber
approximation for the projected weak-lensing power spectrum. We consider
spherical coordinates and the flat-sky approximation, and compute the full
projection as well as first- and second-order Limber approximation. We show
that the second-order Limber approximation is an accurate representation of the full projection, with better than percent level precision for scale $\ell > 3$. 
Since this approximation involves only 1D integrals over the matter power spectrum, it is very fast to
calculate numerically and can readily employed in Monte-Carlo sampling methods
to obtain precision constraints on cosmological parameters.

This paper is organised as follows.  In section~\ref{sec:wl} we provide a pedagogical introduction to weak gravitational lensing theory, projections and power spectra for the flat-sky and spherical cases.  In section~\ref{sec:L2} we derive weak lensing observables using a second-order limber approximation first introduced by \citet{2008PhRvD..78l3506L}.  We compare the shear power spectrum and commonly-used two-point shear correlation function for the full solution to a range of different approximations in section~\ref{sec:comp}, providing cosmological constraints for each case using CFHTLenS data from \citet{CFHTLenS-2pt-notomo} in section~\ref{sec:cfhtlens}.  This paper draws from several sources of literature which have previously reviewed the accuracy of the Limber approximation for weak lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B, 2012MNRAS.422.2854G, 2016arXiv161104954K}.   We present a discussion and comparison of our results to these papers in Appendix~\ref{app:B}.

@@

In this section we review the basic weak-lensing projection expressions, and
compute lensing power spectra for a spherical case, and in the flat-sky
approximation. For completeness we provide a derivations of the weak lensing power spectra in Appendix~\ref{sec:derivations_C}.

@@

To specify tomographic redshift bins $i=0\ldots N_z-1$, we introduce a family
of lensing efficiency functions $q_i$ defined by a corresponding family of
redshift distributions $n_i$ via eq.~(\ref{eq:lens_efficiency}). The resulting
lensing potential is denoted by $\psi_{\ell m, i}$. The tomographic power
spectrum of the lensing potential between two redshift bins $i$ and $j$,
$C_{ij}^\psi$ is then defined by \cite{pee80}
%
\begin{equation}
  \left\langle \psi^{}_{\ell m, i} \, \psi^\ast_{\ell^\prime m^\prime, j} \right\rangle
    = \delta_{\ell \ell^\prime} \delta_{m m^\prime} C^\psi_{ij}(\ell) .
  \label{eq:C_ell_psi}
\end{equation}
%
Using the properties of the spherical harmonics (see
App.~\ref{sec:derivations_C} for details) the power spectrum can be written as
%
\begin{align}
  C_{ij}^\psi(\ell) = & \frac 8 {c^4 \pi} 
  \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} q_i(\chi)
  \int_0^{\chi^\prime_{\rm lim}} \frac{{\rm d}\chi^\prime}{\chi^\prime} q_j(\chi^\prime)
  \int {\rm d} k k^2 \, {\rm j}_\ell(k \chi) {\rm j}_\ell(k \chi^\prime) P_\Phi(k; \chi, \chi^\prime)
  \label{eq:C_ell_phi_Pphi} \\
  = & \frac 8 \pi \pref^2
  \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
  \int_0^{\chi^\prime_{\rm lim}} \frac{{\rm d}\chi^\prime}{\chi^\prime} \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
  \int \frac{{\rm d} k}{k^2} \, {\rm j}_\ell(k \chi) {\rm j}_\ell(k \chi^\prime) P_{\rm m}(k; \chi, \chi^\prime) ;
  \label{eq:C_ell_phi_Pm}
\end{align}
%
where for convenience we defined the normalisation constant $\pref$ as
%
\begin{equation}
  \pref = \frac 3 2 \Omega_{\rm m} \left(\frac{H_0} c\right)^2.
  \label{eq:pref}
\end{equation}
%
The first line expresses $C_{ij}^\psi$ in terms of the 3D potential power spectrum $P_\Phi$, defined as
%
\begin{align}
  \left\langle \hat \Phi(\vec k; \chi) \hat \Phi^\ast(\vec k^\prime; \chi^\prime) \right\rangle
    = & (2\pi)^3 \delta_{\rm D}(\vec k - \vec k^\prime) P_\Phi(k; \chi, \chi^\prime).
    %\nonumber \\
    %= & (2\pi)^3 \delta_{\rm D}(\vec k - \vec k^\prime) \pref^2 k^{-4} a^{-1}(\chi) a^{-1}(\chi^\prime)
      %P_{\rm m}(k; \chi, \chi^\prime).
  \label{eq:p_phi}
\end{align}
%
The second line uses the 3D matter density power spectrum $P_{\rm m}$, which is defined analogously as
%
\begin{align}
  \left\langle \hat \delta(\vec k; \chi) \hat \delta^\ast(\vec k^\prime; \chi^\prime) \right\rangle
    = & (2\pi)^3 \delta_{\rm D}(\vec k - \vec k^\prime) P_{\rm m}(k; \chi, \chi^\prime),
  \label{eq:p_m}
\end{align}
%
and is
related to $P_\Phi$ via the absolute square of the Poisson equation (\ref{eq:poisson}).

@@

The tomographic shear power spectrum, in analogy to (\ref{eq:C_ell_phi_Pm}), is defined by
%
\begin{equation}
  \left\langle _2\gamma^{}_{\ell m, i} \; {}_2\gamma^\ast_{\ell^\prime m^\prime, j} \right\rangle
    = \delta_{\ell \ell^\prime} \delta_{m m^\prime} C^\gamma_{ij}(\ell).
  \label{eq:C_ell_gamma}
\end{equation}
%
For a flat Universe, this is given by
%
\begin{align}
  C^\gamma_{ij}(\ell) = \frac 1 4 \ellbar^2(\ell, 2) \, C^\psi_{ij}(\ell)
                 = & \frac 2 \pi \, \ellbar^2(\ell, 2) \, \pref^2
                 \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
                \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi^\prime}{\chi^\prime}
                \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
                %\nonumber \\
                %& \times
                \int_0^\infty \frac{{\rm d} k}{k^2} \, P_{\rm m}(k, \chi, \chi^\prime) \,
                {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime) .
  \label{eq:C_ell_full}
\end{align}
%
The spherical prefactor for the full projection power spectrum is $p(\ell) =
\ellbar^2(\ell, 2)$, which will be modified under flat-sky and Limber
approximations below.

@@

We follow \cite{2008PhRvD..78l3506L} who derive the second-order Limber
expansion for general projections from 3D to 2D scalar fields in the spherical,
all-sky case. First, we use the identity of Bessel functions
%
\begin{equation}
  {\rm j}_\ell(x) = \sqrt{\frac{\pi}{2x}} {\rm J}_{\ell + 1/2}(x)
\end{equation}
%
in eq.~(\ref{eq:C_ell_full}). Next, \cite{2008PhRvD..78l3506L} solve
integrals of the form
%
\begin{equation}
  \int_0^\infty {\rm d} \chi f(\chi) {\rm J}_{\ell + 1/2}(k \chi)
  = \int_0^\infty {\rm d} x k^{-1} f(x/k) {\rm J}_{\ell + 1/2}(x)
  \label{eq:int_dchi}
\end{equation}
%
by performing a Taylor expansion of the function $f$ around $x = k \chi = \nu$, where
the Bessel function has its approximate maximum.

@@

\subsection{Flat sky}

The extended flat-sky Limber approximation is readily derived from the
spherical case, by replacing the prefactor $\ellbar^2(\ell, 2)$ with $\ell^4$,
%
\begin{align}
  P^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ell^4}{\nu^4} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
  P_{\rm m}\left(k = \frac{\nu}{\chi}; \chi\right);
  \label{eq:P_ell_limber1}
  \\
    P^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ell^4}{\nu^4} \, \pref^2
    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(k = \frac\nu\chi; \chi\right)
    %\nonumber \\
    %& \times
    \frac{a(\chi)}{2 D^{-1}_+(\chi)} \chi^{3/2} \left[ q^{}_i f^{\prime\prime}_{{\rm s}j} + f^{\prime\prime}_{{\rm s}i} q^{}_j  
      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_{{\rm s}j} + f^{\prime\prime\prime}_{{\rm s}i} q^{}_j
      \right)
    \right](\chi)
  \label{eq:P_ell_limber2}
\end{align}
%
Different further approximations are commonly made for the prefactor $p(\ell) = \ell^4/\nu^4$ and $\nu(\ell)$.
%
\begin{enumerate}
  \item $p(\ell) = 1$, this corresponds to setting $\nu(\ell) = \ell$, and is the standard Limber approximation.
    Until recently, i.e.~for all pre-2014 CFHTlenS results, this was the approximation of choice.
  \item $p(\ell) = \ell^4/\nu^4(\ell)$ with $\nu(\ell) = \ell + 1/2$. This corresponds to the extended Limber
    approximation; however the following case is typically employed:
  \item $p(\ell) = 1$, but as the argument of the 3D power spectrum $\nu = \ell + 1/2$. This is a hybrid between
    standard and extended Limber approximation, and was used in \cite{KiDS-450,joudaki/etal:2016}. As is shown
    later, this is a much better approximation than case 2.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\subsection{Comparison of the approximations}
\label{sec:comp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Application to CFHTLenS data}
\label{sec:cfhtlens}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Conclusions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and comparison to previously published work}
\label{app:B}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

We compute the spherical-sky weak-lensing power spectrum of the shear and
convergence. We discuss various approximations, such as flat-sky, first- and
second-order Limber equations for the projection. We find that the impact of adopting 
these approximations are negligible when constraining cosmological parameters from 
current weak lensing surveys.
This is demonstrated using data from the Canada-France-Hawaii Lensing Survey (CFHTLenS). 
We find that the reported tension with Planck CMB temperature anisotropy results cannot be alleviated, in
contrast to the recent claim made by \citet{2016arXiv161104954K}. 
For future large-scale surveys with unprecedented precision, we show that the spherical
second-order Limber approximation will provide sufficient accuracy, as it is in 
agreement with the full projection at the percent level for $\ell > 3$.  
In the spirit of reproducible research, our numerical implementation of all approximations
and the full projection are publicly available within the package
\textsc{nicaea} at \texttt{http://www.cosmostat.org/software/nicaea}.

@@

The measurement of weak gravitational lensing by large-scale structures
provides a powerful cosmological probe of dark matter, dark energy, and
modifications to gravity.  As such it is the primary science goal of several
current (KiDS, HSC, DES) and future (Euclid, LSST, WFIRST) large-scale surveys.
Interest in the results from these surveys is high as statistically significant
deviations have been found between the cosmological parameter constraints from
the CMB Planck experiment \citep{2015arXiv150201589P} in comparison to weak
lensing constraints from both the Kilo-Degree Survey \citep[KiDS;][]{KiDS-450}
and the Canada-France-Hawaii Telescope Lensing Survey
\citep[CFHTLenS;][]{joudaki/etal:2016}.  If the source of this tension is not
a result of so-far unconsidered sources of systematic errors in one or all
experiments, extensions to the standard flat $\Lambda$CDM cosmological models
need to be considered. \citet{joudaki/etal:2017} have shown, for example, that
the tension can be resolved with an evolving dark energy model.

In the era of the upcoming large surveys that will provide measurements of
cosmic shear with unprecedented precision, one needs to revisit the theoretical
model predictions of the observables to ensure that the accuracy of the
models meet the upcoming data. In this paper, we examine the widely used Limber
approximation for the projected weak-lensing power spectrum. We consider
spherical coordinates and the flat-sky approximation, and compute the full
projection as well as first- and second-order Limber approximation. We show
that the latter is an excellent approximation of the full projection. Since it
involves only 1D integrals over the matter power spectrum, it is very fast to
calculate numerically and can readily employed in Monte-Carlo sampling methods
to obtain precision constraints on cosmological parameters.

This paper is organised as follows.  In section~\ref{sec:wl} we provide a pedagogical introduction to weak gravitational lensing theory, projections and power spectra for the flat-sky and spherical cases.  In section~\ref{sec:L2} we derive weak lensing observables using a second-order limber approximation first introduced by \citet{2008PhRvD..78l3506L}.  We compare the shear power spectrum and commonly-used two-point shear correlation function for a range of different approximations in section~\ref{sec:comp}, providing cosmological constraints for each case using CFHTLenS data from \citet{CFHTLenS-2pt-notomo} in section~\ref{sec:cfhtlens}.  This paper draws from several sources of literature which have previously reviewed the accuracy of the Limber approximation for weak lensing studies, namely \citet{2008PhRvD..78d3002S,2012PhRvD..86b3001B, 2012MNRAS.422.2854G}.

@@

In this section we review the basic weak-lensing projection expressions, and
compute lensing power spectra for a spherical case, and in the flat-sky
approximation. Derivations for those expressions can be found in the appendix.

@@

To specify tomographic redshift bins $i=0\ldots N_z-1$, we introduce a family
of lensing efficiency functions $q_i$ defined by a corresponding family of
redshift distributions $n_i$ via eq.~(\ref{eq:lens_efficiency}). The resulting
lensing potential is denoted by $\psi_{\ell m, i}$. The tomographic power
spectrum of the lensing potential between two redshift bins $i$ and $j$,
$C_{ij}^\psi$ is then defined by \cite{pee80}
%
\begin{equation}
  \left\langle \psi^{}_{\ell m, i} \, \psi^\ast_{\ell^\prime m^\prime, j} \right\rangle
    = \delta_{\ell \ell^\prime} \delta_{m m^\prime} C^\psi_{ij}(\ell) .
  \label{eq:C_ell_psi}
\end{equation}
%
Using the properties of the spherical harmonics (see
App.~\ref{sec:derivations_C} for details) the power spectrum can be written as
%
\begin{align}
  C_{ij}^\psi(\ell) = & \frac 8 {c^4 \pi} 
  \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} q_i(\chi)
  \int_0^{\chi^\prime_{\rm lim}} \frac{{\rm d}\chi^\prime}{\chi^\prime} q_j(\chi^\prime)
  \int {\rm d} k k^2 \, {\rm j}_\ell(k \chi) {\rm j}_\ell(k \chi^\prime) P_\Phi(k; \chi, \chi^\prime)
  \label{eq:C_ell_phi_Pphi} \\
  = & \frac 8 \pi \pref^2
  \int_0^{\chi_{\rm lim}} \frac{{\rm d}\chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
  \int_0^{\chi^\prime_{\rm lim}} \frac{{\rm d}\chi^\prime}{\chi^\prime} \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
  \int \frac{{\rm d} k}{k^2} \, {\rm j}_\ell(k \chi) {\rm j}_\ell(k \chi^\prime) P_{\rm m}(k; \chi, \chi^\prime) ;
  \label{eq:C_ell_phi_Pm}
\end{align}
%
where ${\rm j}_\ell$ it the spherical Bessel function of order $\ell$. For
convenience we defined the normalisation constant $\pref$ as
%
\begin{equation}
  \pref = \frac 3 2 \Omega_{\rm m} \left(\frac{H_0} c\right)^2.
  \label{eq:pref}
\end{equation}
%
The first line expresses $C_{ij}^\psi$ in terms of the 3D potential power spectrum $P_\Phi$, defined as
%
\begin{align}
  \left\langle \hat \Phi(\vec k; \chi) \hat \Phi^\ast(\vec k^\prime; \chi^\prime) \right\rangle
    = & (2\pi)^3 \delta_{\rm D}(\vec k - \vec k^\prime) P_\Phi(k; \chi, \chi^\prime).
    %\nonumber \\
    %= & (2\pi)^3 \delta_{\rm D}(\vec k - \vec k^\prime) \pref^2 k^{-4} a^{-1}(\chi) a^{-1}(\chi^\prime)
      %P_{\rm m}(k; \chi, \chi^\prime).
  \label{eq:p_phi}
\end{align}
%
The second line uses the 3D matter density power spectrum $P_{\rm m}$, which is defined analogously as
%
\begin{align}
  \left\langle \hat \delta(\vec k; \chi) \hat \delta^\ast(\vec k^\prime; \chi^\prime) \right\rangle
    = & (2\pi)^3 \delta_{\rm D}(\vec k - \vec k^\prime) P_{\rm m}(k; \chi, \chi^\prime),
  \label{eq:p_m}
\end{align}
%
and is
related to $P_\Phi$ via the absolute square of the Poisson equation (\ref{eq:poisson}).

@@

The tomographic shear power spectrum, in analogy to (\ref{eq:C_ell_phi_Pm}), is defined by
%
\begin{equation}
  \left\langle _2\gamma^{}_{\ell m, i} \; {}_2\gamma^\ast_{\ell^\prime m^\prime, j} \right\rangle
    = \delta_{\ell \ell^\prime} \delta_{m m^\prime} C^\gamma_{ij}(\ell).
  \label{eq:C_ell_gamma}
\end{equation}
%
For a flat Universe, this is given by
%
\begin{align}
  C^\gamma_{ij}(\ell) = \frac 1 4 \ellbar^2(\ell, 2) \, C^\psi_{ij}(\ell)
                 = & \frac 2 \pi \, \ellbar^2(\ell, 2) \, \pref^2
                 \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi}{\chi} \frac{q_i(\chi)}{a(\chi)}
                \int_{0}^{\chi_{\rm lim}} \frac{\rm d \chi^\prime}{\chi^\prime}
                \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
                %\nonumber \\
                %& \times
                \int_0^\infty \frac{{\rm d} k}{k^2} \, P_{\rm m}(k, \chi, \chi^\prime) \,
                {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime) .
  \label{eq:C_ell_full}
\end{align}
%
The spherical prefactor for the full projection power spectrum is $p(\ell) :=
\ellbar^2(\ell, 2)$, which will be modified under flat-sky and Limber
approximations below.

@@

We follow \cite{2008PhRvD..78l3506L} who derive the second-order Limber
expansion for general projections from 3D to 2D scalar fields in the spherical,
all-sky case. First, we use the identity of Bessel functions
%
\begin{equation}
  {\rm j}_\ell(x) = \sqrt{\frac{\pi}{2x}} {\rm J}_{\ell + 1/2}(x)
\end{equation}
%
in eq.~(\ref{eq:C_ell_full}), where ${\rm J}_\ell$ is the first-kind Bessel
function of order $\ell$. Next, \cite{2008PhRvD..78l3506L} solve integrals of
the form
%
\begin{equation}
  \int_0^\infty {\rm d} \chi f(\chi) {\rm J}_{\ell + 1/2}(k \chi)
  = \int_0^\infty {\rm d} x k^{-1} f(x/k) {\rm J}_{\ell + 1/2}(x)
  \label{eq:int_dchi}
\end{equation}
%
by performing a Taylor expansion of the function $f$ around $x = k \chi = \nu$, where
the Bessel function has its approximate maximum.

@@

\subsection{Flat sky}
\label{sec:Limber_flat_sky}

The extended flat-sky Limber approximation is readily derived from the
spherical case, by replacing the prefactor $\ellbar^2(\ell, 2)$ with $\ell^4$,
%
\begin{align}
  P^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ell^4}{\nu^4} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
  P_{\rm m}\left(k = \frac{\nu}{\chi}; \chi\right);
  \label{eq:P_ell_limber1}
  \\
    P^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ell^4}{\nu^4} \, \pref^2
    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(k = \frac\nu\chi; \chi\right)
    %\nonumber \\
    %& \times
    \frac{a(\chi)}{2 D^{-1}_+(\chi)} \chi^{3/2} \left[ q^{}_i f^{\prime\prime}_{{\rm s}j} + f^{\prime\prime}_{{\rm s}i} q^{}_j  
      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_{{\rm s}j} + f^{\prime\prime\prime}_{{\rm s}i} q^{}_j
      \right)
    \right](\chi)
  \label{eq:P_ell_limber2}
\end{align}
%
Different further approximations are commonly made for the prefactor $p(\ell) = \ell^4/\nu^4$ and $\nu(\ell)$:
%
\begin{enumerate}
  \item $p(\ell) = 1$, this corresponds to setting $\nu(\ell) = \ell$, and is the standard Limber approximation.
    Until recently, i.e.~for all pre-2014 CFHTlenS results, this was the approximation of choice.
  \item $p(\ell) = \ell^4/(\ell + 1/2)^4$. This corresponds to the extended Limber
    approximation with $\nu(\ell) = \ell + 1/2$; however the following case is typically employed:
  \item $p(\ell) = 1$, but as the argument of the 3D power spectrum $\nu = \ell + 1/2$. This is a hybrid between
    standard and extended Limber approximation, and was used in \cite{KiDS-450,joudaki/etal:2016}. As is shown
    later, this is a much better approximation than case 2.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comparison of the approximations}
\label{sec:comp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Application to CFHTLenS data}
\label{sec:cfhtlens}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion and comparison to previously published work}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
